Pool Model

### 2025-08-21 pool_model.tex
mutual inhibition: use I notation for inhibitor instead of T

    \mathcal{B}(G)&=&\frac{\alpha}{1+KG}. 
This corresponds to the case $T\sim G$, where $T$ is the toxin produced.
If the toxin accumulates one needs to replace $G$ by $\int G dt$. Keeping it simple yields:

@@

@@

Furthermore, Sometimes neighbors can benefit from a certain behavior without expressing it by itself, so-called 'social cheaters'~\cite{rainey_evolution_2003}.

>>>>

    \mathcal{B}(G)&=&\frac{\alpha}{1+KI(G)},
where $I$ is the concentration of the inhibiting metabolic byproduct producing during bacterial growth.

@@

Note that if the toxin accumulates, i.e., $\dot I \sim G$,  one needs to replace $G$ by $\int G dt$.

@@

Furthermore, neighbors can also benefit from a certain behavior without expressing it by itself, so-called 'social cheaters'~\cite{rainey_evolution_2003}.
